\cvsection{Education}
    \cvevent{Radio engineering and computer technology}
        {\href{https://mipt.ru}{Moscow Institute of Physics and Technology}}
        {sept. 2020 -- now}{}

    \begin{itemize}
        \item Bachelor's CGPA 9.41/10, top 1 department graduates, top 4 university graduates.
        \item Bachelor thesis topic: \href{https://github.com/Vokerlee/macfm-governor-thesis/blob/master/thesis/ru/thesis.pdf}
                   {"Memory aware CPU frequency scaling policy in Linux kernel"}.
        \item Master's CGPA 9.47/10.
        \item Master thesis topic: in progress.
    \end{itemize}

\cvsection{Technical Skills}
    \cvsubsection{Programming languages / Architectures}
    C11, C++20, Python / RISC-V, x86-64, ARM64
    \smallskip

    \cvsubsection{Core fields}
        \begin{itemize}
            \item Computer system microarchitecture \& simulation.
            \item Linux-API system programming.
        \end{itemize}
    \smallskip

     \cvsubsection{Actual fields}
        \begin{itemize}
            \item Linux kernel programming (scheduler \& concurrency primitives).
            \item Neural networks hardware-based optimizations.
        \end{itemize}
    \smallskip

     \cvsubsection{Other fields}
        \begin{itemize}
            \item \href{https://github.com/Vokerlee/machine-learning-mipt}{Machine learning}.
            \item \href{https://github.com/Vokerlee/llvm-practice}{Compilers internals (LLVM)}.
            \item \href{https://github.com/Vokerlee/computational-maths-mipt}{Computational maths}.
        \end{itemize}
    \smallskip

    \cvsubsection{Technologies}
    \href{https://github.com/Vokerlee/linux-api-course}{Linux API},
    \href{https://github.com/Vokerlee/parallel-computing-mipt}{MPI, OpenMP}
    \smallskip

    \cvsubsection{Languages}
    English -- upper intermediate
    \smallskip

\cvsection{Extra info}
    \begin{itemize}
        \item Cryptocurrency algo-trading average enjoyer
        \item Member of the national team for the International Physics Olympiad 2020 (cancelled due to Covid19)
        \item Tutor in introduction to compilers \& x86-64 architecture cources in 2021/2022
        \item Powerlifting enjoyer
    \end{itemize}

    % \cvevent{}{}{}{}
    % \vspace{-1mm}
    % \cvevent{}{}{}{}
    % \vspace{-1mm}
    % \cvevent{}{}{}{}
